---
title: "Homework 6 "
author: "Linshen Cai"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(purrr)
library(ggplot2)
library(mgcv)
library(broom)
set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem3

```{r}

# Data Preprocessing
birthweight <- read_csv("./data/birthweight.csv") %>%
  mutate(
    babysex = factor(ifelse(babysex == 1, "male", "female")),
    frace = factor(case_when(
      frace == 1 ~ "White",
      frace == 2 ~ "Black",
      frace == 3 ~ "Asian",
      frace == 4 ~ "Puerto Rican",
      frace == 8 ~ "Other",
      frace == 9 ~ "Unknown")),
    malform = factor(ifelse(malform == 0, "absent", "present")),
    mrace = factor(case_when(
      mrace == 1 ~ "White",
      mrace == 2 ~ "Black",
      mrace == 3 ~ "Asian",
      mrace == 4 ~ "Puerto Rican",
      mrace == 8 ~ "Other"
    ))
  )

# Model Fitting
my_lm <- lm(bwt ~ fincome * menarche + fincome * momage + menarche * momage, data = birthweight)
tidy_results <- tidy(my_lm) %>% select(term, estimate, p.value)
residual_plot <- ggplot(add_residuals(birthweight, my_lm), aes(x = bwt, y = resid)) + geom_point()

# Cross-Validation
cv_df <- crossv_mc(birthweight, 100) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble),
    linear_mod = map(train, ~lm(bwt ~ blength + gaweeks, data = .)),
    pwl_mod = map(train, ~lm(bwt ~ bhead * blength + bhead * babysex + blength * babysex, data = .)),
    mypwl_mod = map(train, ~lm(bwt ~ fincome * menarche + fincome * momage + menarche * momage, data = .))
  ) %>%
  mutate(
    rmse_linear = map2_dbl(linear_mod, test, ~rmse(model = .x, data = .y)),
    rmse_pwl = map2_dbl(pwl_mod, test, ~rmse(model = .x, data = .y)),
    rmse_mypwl = map2_dbl(mypwl_mod, test, ~rmse(model = .x, data = .y))
  )

# Visualization of Cross-Validation Results
cv_violin_plot <- cv_df %>%
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>%
  mutate(model = fct_inorder(model)) %>%
  ggplot(aes(x = model, y = rmse)) + geom_violin()

# Display Results
print(tidy_results %>% knitr::kable(digit = 3))
print(residual_plot)
print(cv_violin_plot)

```

Preprocessing the birthweight information, which involves recoding certain categories and transforming categorical variables to factors, is the first step in the modeling process. Next, a linear regression model is fitted to predict the birth weight by taking into account the interactions between the mother's age, menarche, and financial income. Extracted model coefficients, estimates, and p-values are shown in a tabular manner. A scatter plot is utilized to visualize residuals. Then, three models are evaluated using 100 iterations of cross-validation: one with basic predictors, one with extra interactions, and one with the original interaction terms. The violin shape for the distribution of RMSE for each model is plotted. The pwl model has the smallest rmse and variance.





